Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-01-21 Manuscript/FLPhish(Trans).tex
FLPhish-threshold换掉

\maketitle
% FLPhish           scheme
% FL                architecture
% other robust FL   schme
% Ensemble FL       architecture
% FLPhish-threshold aggregation rule
% FLPhish-weight    aggregation rule
\begin{abstract}
  With the emerging demand for personal privacy, FL is becoming a popular distributed machine learning paradigm. Nonetheless, the implementation of FL is still vulnerable to Byzantine attacks, which can bring significant hazards during the global model aggregation process, and is extremely difficult to defend. In this paper, we present a reputation-based robust-FL scheme (FLPhish) for defending Byzantine attacks under the Ensemble FL architecture. First, we design a new Ensemble FL architecture, which is compatible with different deep learning models for different clients. Second, we craft a phishing mechanism for the Ensemble FL architecture to identify Byzantine attacks. Furthermore, a reputation mechanism based on the Bayesian inference is presented to measure each client's level of confidence. Last, we propose two aggregation rules with FLPhish: FLPhish-threshold and FLPhish-weight. FLPhish is tested with different fractions of Byzantine clients and different degrees of distribution imbalance. Extensive experiments under different settings demonstrate that the proposed FLPhish achieves great efficacy in resisting Byzantine attacks in Ensemble FL.
\end{abstract}

@@

\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine clients under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. In the presence of a bounded number of malicious clients, Byzantine-robust approaches aim to develop a global model with high accuracy. According to their different mechanisms, we divide Byzantine-robust approaches into two major types. The first (named Byzantine-Detection) is based on the creation of a Byzantine-robust aggregation rule that distinguishes questionable customers from benign clients. The server then eliminates the suspected clients' gradient updates from the aggregation process. For instance, in the DRACO scheme proposed by Chen \textit{et al.}, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another type of Byzantine-robust approach (named Byzantine-Tolerance) aims to ensure that the aggregation process is tolerant of Byzantine clients' poisoned updates without excluding Byzantine clients like Median \cite{ref_16_defense}. In Median, The FL server sorts the values of each parameter and selects the median value of each parameter as the value to be used in global model updates. Based on the above analysis, in this paper, we present a novel reputation-based phishing scheme (called FLPhish) to defend against Byzantine attacks in Ensemble FL. Our contributions are four-fold:
\begin{itemize}
  \item We design a new FL architecture, Ensemble Federated Learning (called Ensemble FL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL. This architecture is flexible by for it is compatible with different deep learning models in different clients.
  \item We craft a `phishing' method based on Ensemble FL to detect Byzantine attacks. The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the Ensemble FL system, which preserves the security of Ensemble FL.
  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients, which helps FLPhish identify the Byzantine clients with higher accuracy.
  \item We propose two aggregation rules, called FLPhish-threshold and FLPhish-weight, to aggregate the predictions of the FL clients, based on reputation mechanism, which contribute to the robustness of FLPhish. That is, FLPhish-threshold identifies the clients with low reputation values as Byzantine clients, while FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate in the aggregation process.
\end{itemize}

@@

\par \textit{1)} Typical FL architecture has many drawbacks including not being compatible with different deep learning models in different clients and introducing high communication costs. Thus, inspired by the idea of ensemble learning, we build a new FL architecture called Ensemble FL. It reduces the network transfer cost and provides more opportunities for us to counter Byzantine attacks in FL.
\par \textit{2)} The proposed Ensemble FL architecture still lacks effective protection mechanism against Byzantine attacks. Since the clients in FL can not be fully trusted, we urgently require an efficient way to tackle malicious Byzantine clients. Thus, we present a phishing-based mechanism to guard against Byzantine attacks in our proposed Ensemble FL system.
\par \textit{3)} As the performance of each client remains not stable in each iteration, it is important for our scheme to accurately measure each client's level of confidence in the long term. Therefore, we further propose an effective Bayesian inference-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.
\par \textit{4)} With each client's level of confidence measured accurately via reputation mechanism, the aggregation rule of the Ensemble FL architecture should be reconsidered on the basis of each client's reputation. Furthermore, we propose two aggregation rules in FLPhish, FLPhish-threshold, and FLPhish-weight to aggregate the predictions of the FL clients, which can further enhance FLPhish's defending ability against Byzantine attacks.

@@

\subsection{Aggregation Rules}
Based on our reputation mechanism, we propose our Byzantine-tolerant aggregation rules: FLPhish-threshold and FLPhish-weight.
\subsubsection{{FLPhish-threshold}}
FLPhish-threshold functions as the aggregation rules to identify the clients, whose reputation is lower than the reputation threshold. Then the server discards the Byzantine clients and aggregates the global model using the survived clients' updates. The server identifies the client ${c_{i}}$ whose reputation is lower than the threshold $\tau$ as Byzantine clients, and gives it a aggregation weight as
\begin{equation}
  \omega_{i}=\begin{cases}
    1 & \text{ if } x\geq \tau \\ 
    0 & \text{ if } x< \tau 
    \end{cases}.
\end{equation} 
The aggregated knowledge is given by
\begin{equation}
  \mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i\times \omega_{i},
\end{equation}
\begin{equation}
  \mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t}).
\end{equation} 
\subsubsection{{FLPhish-weight}}
Unlike FLPhish-threshold, FLPhish-weight does not discard the potential Byzantine clients' updates. On the contrary, it enables the Byzantine clients to participate the aggregation using its reputation value as the aggregation weight. Due to our reputation mechanism, the Byzantine clients are offered a low reputation, so it has a lower influence on the aggregation process.
Give a reputation list $R=\left | x_{1},x_{1},x_{1},\cdots ,x_{n-1},x_{n} \right |$, the prediction results is 
  \begin{equation}
    \mathbf{k_i^t}=\begin{vmatrix}
      p_{1,1} & p_{1,2} & \cdots  & p_{1,g-1} & p_{1,g}\\ 
      \vdots  & \vdots & \ddots  & \vdots & \vdots\\ 
      p_{n,1} & p_{n,2} & \cdots  & p_{n,g-1} & p_{n,g}
      \end{vmatrix},
  \end{equation}
  Meanwhile, FLPhish-weight computes the aggregated knowledge, which is
    \begin{equation}
    \mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i\times x_{i}.
  \end{equation}
  Then the server $s$ uses the aggregated knowledge $\mathbf{\hat{k}^t}$ to get the labels
  \begin{equation}
    \mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t}).
  \end{equation} 
In a word, FLPhish-weight does not identify the Byzantine clients but treats the clients with a low reputation as `bad' clients and gives them lower weights.

@@

\section{Performance Evaluation}
In this section, we experimentally evaluate our FLPhish against untargeted attacks under different experiment settings. Furthermore, we compare FLPhish's performance with FedAvg, Median \cite{ref_13_defense}, and Trimmed Mean \cite{ref_13_defense}'s performance, and the evaluation results demonstrate that FLPhish outperforms FedAvg in defending against Byzantine attacks.

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
\begin{table}[t]
  \renewcommand\arraystretch{1.5}
  \centering
  \caption{Evaluated Scheme}
  \resizebox{0.5\textwidth}{!}{%
  \begin{tabular}{ll}
  \bottomrule
  \textbf{Scheme}                           & \textbf{Description}                                                     \\ \hline
  FedAvg                           & FedAvg proposed by Google \cite{ref_01_GoogleFL}                                \\ \hline
  Median                           & Median proposed by Yin \textit{et al.} \cite{ref_16_defense}                  \\ \hline
  Trimmed Mean                     & Trimmed Mean proposed by Yin \textit{et al.} \cite{ref_16_defense}            \\ \hline
  FLPhish($\tau=0.1$) & FLPhish-threshold with threshold $\tau=0.1$ \\ \hline
  FLPhish($\tau=0.2$) & FLPhish-threshold with threshold $\tau=0.2$ \\ \hline
  FLPhish($\tau=0.5$) & FLPhish-threshold with threshold $\tau=0.5$ \\ \hline
  FLPhish(weight)                  & FLPhish-weight                                           \\ \hline
  \end{tabular}%
  }
  \end{table}

@@

  \subsubsection{{\textit{The fraction {$p$} of Byzantine clients}}} We evaluate our FLPhish under the circumstances of different fractions $p$ of Byzantine clients: 0 (no Byzantine clients), 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9.
  \subsubsection{{\textit{The imbalance degree {$q$} of the data}}} According to the previous research \cite{ref_06_model}, we distribute the data in a dataset among all the clients. Giving $M$ classes of data in a dataset, we split the clients into $M$ groups. A client $c$ in group $m$ is provided with data where data $m$ accounts for over $q$ percent. Within the same group, data are uniformly distributed among all the clients. The parameter $q$ controls the distribution inference of clients' local training data. If $q=\frac{1}{M}$, the clients' local training data are independent and identically distributed. We evaluate our FLPhish on three different $q$: 0.1 (IID), 0.2, 0.5, 0.6, 0.7, and 0.8.
  \subsubsection{{\textit{The number of clients}}} The number of clients is set to be 50 in our experiment.
  \subsubsection{{\textit{The local CNN model used by clients}}} ResNet is employed to perform deep learning tasks in our local client.
  \subsubsection{{\textit{The datasets {$d$}}}} We take three different datasets as our experiment datasets: \begin{itemize}
      \item MNIST: MNIST is a 10-class digit image classification dataset consisting of 60,000 training examples and 10,000 testing examples.
      \item Fashion-MNIST: Fashion-MNIST is a 10-class fashion image classification dataset. It has a predefined training set of 60,000 fashion images and a testing set of 10,000 fashion images.
      \item CIFAR-10: CIFAR-10 is a color image classification dataset. It has predefined 50,000 training examples and 10,000 testing examples. Each example belongs to one of the 10 classes.
  \end{itemize}

@@

  \par Each client has 1,000 samples taken from the training dataset. Among the samples, 800 of them are used as training datasets, while another 200 are taken as test datasets. And the server has 10000 testing examples from the testing dataset. 
  \subsubsection{\textit{Evaluated Byzantine Attacks}} We evaluate our FLPhish-weight and FLPhish-threshold against two Byzantine attacks:
  \begin{itemize}
    \item Untargeted Byzantine Attacks: For each Byzantine client, it mislabels the data $l$ to $(l-1)\ mod\ M$ to launch the attacks against FLPhish. The attack is known as the Label-flipping attack. 
    \item Random Byzantine Attacks: For each Byzantine client, it mislabels the labels by returning a randomly chosen result.
    \end{itemize}

@@

  \subsection{Performance Comparison under Random Attacks}
  From Fig. \ref{fig_exp_extreme}-\ref{fig_table_byzantines_random}, we can see that random Byzantine attacks have poor performance against FLPhish-weight and FLPhish-threshold (threshold=0.1, 0.2). We refer from the result that a random Byzantine attack has a drawback that it can not gather its influence at one data point as untargeted Byzantine attackers do. Meanwhile, we can see that it has good results in attacking FLPhish-threshold(threshold=0.5) in the CIFAR-10 dataset. From Fig. \ref{fig_exp_reputation}, we can see that the reputation of benign clients in CIFAR-10 experiments rapidly falls under the threshold of 0.5 due to the complexity of the tasks. With the increase of imbalance degree value $q$, the reputation of the benign clients falls more rapidly in the experiments of the CIFAR-10 dataset than in the experiments of the MNIST and the Fashion-MNIST dataset. As benign clients' reputations in the experiments of the CIFAR-10 dataset become under the threshold $\tau$ of 0.5, they are identified as malicious Byzantine clients as well. As many benign clients are falsely identified as Byzantine attackers, the FL server lacks enough trusted FL clients to assist the aggregation, therefore causing a bad performance of FLPhish-threshold (threshold=0.5). Meanwhile, we can see that FLPhish-threshold (threshold=0.1), FLPhish-threshold (threshold=0.2), and FLPhish-weight stood still against the random Byzantine attacks. The results indicate that the value of the threshold $\tau$ should be considered carefully in the application in some complex tasks.

  \subsection{{Performance Comparison under Untargeted Attacks}} We further evaluate FLPhish towards untargeted Byzantine attacks in Ensemble FL.

    \subsubsection{\ul{Performance Comparison with Different Distributions}} We evaluate our FLPhish-threshold and FLPhish-weight under the experiment setting where the Byzantine client portion is a fixed value of 0.5 and distribution imbalance value $q$ is different across the experiments. The experiment results are shown in Fig. \ref{fig_table_imbalances_untargeted}. We can observe that both the FLPhish-threshold and FLPhish-weight outperform baseline until the imbalance degree $q$ reaches 0.8. The imbalance degree $q$ of 0.8 means that the distribution of data becomes extremely non-IID. The performance of the FLPhish-threshold with a threshold=0.5 rapidly falls in this case. When facing the distribution of imbalance degree $q=0.8$, each client performs badly, bringing a decline to its reputation. The rise of imbalance degree brings an explosive decline in the global model's accuracy. The accuracy of the global model under the FLPhish-threshold of threshold=0.5 stays to be 0.1 in the whole learning process. It means that the FLPhish-threshold of threshold=0.5 identifies all the clients as Byzantine clients, making the aggregation process invalid. We can see that the FLPhish-threshold of threshold=0.2 outperforms others. When the distribution becomes non-IID, the threshold of FLPhish-threshold should be set to a lower value to avoid a high false-negative rate. In the experiment of MNIST, it should be set to 0.2. Meanwhile, the performance of FLPhish-weight remains stable under different imbalance degrees.

    \subsubsection{\ul{Performance Comparison with Different Fractions of Byzantine Clients}} Different fractions of Byzantine clients are taken into account as well. Figure. \ref{fig_table_byzantines_untargeted} shows that the accuracy for FedAvg, Median, Trimmed Mean, and Ensemble FL without any defense mechanisms begins to fall rapidly when the Byzantine portion reaches nearly 50\%. Furthermore, FedAvg, Median, and Trimmed Mean perform extremely invalidly (the accuracy falls below 1\%) when encountered with high fractions of Byzantine attackers. In comparison, FLPhish's (including FLPhish-threshold and FLPhish-weight) performance under various thresholds maintain a high level of performance as the portion grows. Both FLPhish-threshold and FLPhish-weight effectively detect Byzantine clients and accurately discard them from the aggregation process. The global model can be successfully trained without the involvement of Byzantine clients during the aggregation procedures. Furthermore, the data show that FLPhish-threshold with threshold=0.1 performs worse than the other two. This is since the threshold=0.1 is far too low to adequately detect Byzantine clients. Though the Byzantine attackers try to make the right predictions of the public dataset and then send the opposite wrong predictions to the FL server. But they also make wrong predictions first and coincidentally transfer the opposite right predictions to the FL server. Thus the reputation values of some Byzantine clients, in particular, can exceed 0.1. It indicates that if the threshold is not well set, Byzantine clients can avoid being detected by FLPhish-threshold. As the fractions of Byzantine clients go over the threshold of 50\%, the harm brought by untargeted Byzantine attacks increase rapidly for they outnumber the fractions of the benign clients. In the meantime, FLPhish-weight shows stable performance whenever the fractions of Byzantine clients are.

    \subsection{{Experiment Result Analysis}} Our experiment results demonstrate that both FLPhish-threshold and FLPhish-weight outperform FedAvg, Median \cite{ref_13_defense} and Trimmed Mean \cite{ref_13_defense} on defending against Byzantine attacks in FL. The results also show that the threshold setup has a significant impact on the performance of the FLPhish-threshold. Only when the managers of FL servers have complete knowledge of FL clients (the imbalance degree of each client), can they accurately set the value of the threshold suitably. However, it is not feasible due to the privacy concern of FL. FLPhish-weight, on the other hand, remains constant regardless of the circumstances. FLPhish-weight can let clients with higher performance have a stronger influence on the aggregation process by using the reputation value as the weight. To summarize, FLPhish-weight is a better and more stable aggregation technique than FLPhish-threshold and demonstrates to be a more practical Byzantine defense framework.

@@

In this paper, we have designed an FL architecture, Ensemble Federated Learning in this study, which allows knowledge transferring between the FL server and FL clients via the unlabeled dataset and FL clients' predictions of it. We have crafted the FLPhish technique to make Ensemble FL resistant to Byzantine attacks by using a labeled dataset as `bait' to detect malicious Byzantine clients. Furthermore, we have proposed a reputation technique based on Bayesian inference to determine a client's level of trust. We have also presented two aggregation techniques, FLPhish-threshold and FLPhish-weight, to improve FLPhish's performance. At last, we have tested our suggested FLPhish in a variety of scenarios. The results of the experiment demonstrates the comparable performance of FLPhish in terms of accuracy and robustness under Byzantine attacks in FL. 
\par Our future work will focus on evaluating FLPhish against more advanced Byzantine attacks and improving FLPhish scheme's efficiency.

>>>>

\maketitle
% FLPhish           scheme
% FL                architecture
% other robust FL   schme
% Ensemble FL       architecture
% FLPhish-threshold aggregation rule
% FLPhish-weight    aggregation rule
\begin{abstract}
  With the emerging demand for personal privacy, FL is becoming a popular distributed machine learning paradigm. Nonetheless, the implementation of FL is still vulnerable to Byzantine attacks, which can bring significant hazards during the global model aggregation process, and is extremely difficult to defend. In this paper, we present a reputation-based robust-FL scheme (FLPhish) for defending Byzantine attacks under the Ensemble FL architecture. First, we design a new Ensemble FL architecture, which is compatible with different deep learning models for different clients. Second, we craft a phishing mechanism for the Ensemble FL architecture to identify Byzantine attacks. Furthermore, a reputation mechanism based on the Bayesian inference is presented to measure each client's level of confidence. Last, we propose an aggregation rule with FLPhish: FLPhish-weight. FLPhish is tested with different fractions of Byzantine clients and different degrees of distribution imbalance. Extensive experiments under different settings demonstrate that the proposed FLPhish achieves great efficacy in resisting Byzantine attacks in Ensemble FL.
\end{abstract}

@@

\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine clients under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. In the presence of a bounded number of malicious clients, Byzantine-robust approaches aim to develop a global model with high accuracy. According to their different mechanisms, we divide Byzantine-robust approaches into two major types. The first (named Byzantine-Detection) is based on the creation of a Byzantine-robust aggregation rule that distinguishes questionable customers from benign clients. The server then eliminates the suspected clients' gradient updates from the aggregation process. For instance, in the DRACO scheme proposed by Chen \textit{et al.}, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another type of Byzantine-robust approach (named Byzantine-Tolerance) aims to ensure that the aggregation process is tolerant of Byzantine clients' poisoned updates without excluding Byzantine clients like Median \cite{ref_16_defense}. In Median, The FL server sorts the values of each parameter and selects the median value of each parameter as the value to be used in global model updates. Based on the above analysis, in this paper, we present a novel reputation-based phishing scheme (called FLPhish) to defend against Byzantine attacks in Ensemble FL. Our contributions are four-fold:
\begin{itemize}
  \item We design a new FL architecture, Ensemble Federated Learning (called Ensemble FL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL. This architecture is flexible by for it is compatible with different deep learning models in different clients.
  \item We craft a `phishing' method based on Ensemble FL to detect Byzantine attacks. The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the Ensemble FL system, which preserves the security of Ensemble FL.
  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients, which helps FLPhish identify the Byzantine clients with higher accuracy.
  \item We propose an aggregation rule, called FLPhish-weight, to aggregate the predictions of the FL clients, based on reputation mechanism, which contribute to the robustness of FLPhish. That is, FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate in the aggregation process.
\end{itemize}

@@

\par \textit{1)} Typical FL architecture has many drawbacks including not being compatible with different deep learning models in different clients and introducing high communication costs. Thus, inspired by the idea of ensemble learning, we build a new FL architecture called Ensemble FL. It reduces the network transfer cost and provides more opportunities for us to counter Byzantine attacks in FL.
\par \textit{2)} The proposed Ensemble FL architecture still lacks effective protection mechanism against Byzantine attacks. Since the clients in FL can not be fully trusted, we urgently require an efficient way to tackle malicious Byzantine clients. Thus, we present a phishing-based mechanism to guard against Byzantine attacks in our proposed Ensemble FL system.
\par \textit{3)} As the performance of each client remains not stable in each iteration, it is important for our scheme to accurately measure each client's level of confidence in the long term. Therefore, we further propose an effective Bayesian inference-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.
\par \textit{4)} With each client's level of confidence measured accurately via reputation mechanism, the aggregation rule of the Ensemble FL architecture should be reconsidered on the basis of each client's reputation. Furthermore, we propose an aggregation rules in FLPhish, FLPhish-weight to aggregate the predictions of the FL clients, which can further enhance FLPhish's defending ability against Byzantine attacks.

@@

\subsection{Aggregation Rules}
In our conference version, we designed an aggregation rule which utilizes a threshold to identify the Byzantine clients. While in this work, we propose a new Byzantine-tolerant aggregation rule, FLPhish-weight.
\subsubsection{{FLPhish-weight}}
Unlike the aggregation rule designed in our conference version, FLPhish-weight does not discard the potential Byzantine clients' updates. On the contrary, it enables the Byzantine clients to participate the aggregation using its reputation value as the aggregation weight. Due to our reputation mechanism, the Byzantine clients are offered a low reputation, so it has a lower influence on the aggregation process.
Give a reputation list $R=\left | x_{1},x_{1},x_{1},\cdots ,x_{n-1},x_{n} \right |$, the prediction results is 
  \begin{equation}
    \mathbf{k_i^t}=\begin{vmatrix}
      p_{1,1} & p_{1,2} & \cdots  & p_{1,g-1} & p_{1,g}\\ 
      \vdots  & \vdots & \ddots  & \vdots & \vdots\\ 
      p_{n,1} & p_{n,2} & \cdots  & p_{n,g-1} & p_{n,g}
      \end{vmatrix},
  \end{equation}
  Meanwhile, FLPhish-weight computes the aggregated knowledge, which is
    \begin{equation}
    \mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i\times x_{i}.
  \end{equation}
  Then the server $s$ uses the aggregated knowledge $\mathbf{\hat{k}^t}$ to get the labels
  \begin{equation}
    \mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t}).
  \end{equation} 
In a word, FLPhish-weight does not identify the Byzantine clients but treats the clients with a low reputation as `bad' clients and gives them lower weights.

@@

\section{Performance Evaluation}
In this section, we experimentally evaluate our FLPhish (noted as FLPhish(weight)) against untargeted attacks under different experiment settings. Furthermore, we compare FLPhish(weight)'s performance with FedAvg \cite{ref_01_GoogleFL}, Median \cite{ref_13_defense}, and Trimmed Mean \cite{ref_13_defense}'s performance, and the evaluation results demonstrate that FLPhish(weight) outperforms these schemes in defending against Byzantine attacks. Furthermore, we compare our proposed aggregation rule, FLPhish(weight) with former aggregation rule used in our previous work \cite{li2021flphish}. Our previous work (noted as FLPhish($\tau$)) utilized a threshold to identify the Byzantine clients. Here we set the threshold to 0.1 (noted as FLPhish($\tau=0.1$)), 0.2 (noted as FLPhish($\tau=0.2$)) and 0.5 (noted as FLPhish($\tau=0.5$)).

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
\begin{table}[t]
  \renewcommand\arraystretch{1.5}
  \centering
  \caption{Evaluated Scheme}
  \resizebox{0.5\textwidth}{!}{%
  \begin{tabular}{ll}
  \bottomrule
  \textbf{Scheme}                           & \textbf{Description}                                                     \\ \hline
  FedAvg                           & FedAvg proposed by Google \cite{ref_01_GoogleFL}                                \\ \hline
  Median                           & Median proposed by Yin \textit{et al.} \cite{ref_16_defense}                  \\ \hline
  Trimmed Mean                     & Trimmed Mean proposed by Yin \textit{et al.} \cite{ref_16_defense}            \\ \hline
  FLPhish($\tau=0.1$) & Our conference version with $\tau=0.1$ \cite{li2021flphish} \\ \hline
  FLPhish($\tau=0.2$) & Our conference version with $\tau=0.2$ \cite{li2021flphish} \\ \hline
  FLPhish($\tau=0.5$) & Our conference version with $\tau=0.5$ \cite{li2021flphish} \\ \hline
  FLPhish(weight)                  & The scheme proposed by this work                                          \\ \hline
  \end{tabular}%
  }
  \end{table}

@@

  \subsubsection{{\textit{The fraction {$p$} of Byzantine clients}}} We evaluate our FLPhish(weight) under the circumstances of different fractions $p$ of Byzantine clients: 0 (no Byzantine clients), 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9.
  \subsubsection{{\textit{The imbalance degree {$q$} of the data}}} According to the previous research \cite{ref_06_model}, we distribute the data in a dataset among all the clients. Giving $M$ classes of data in a dataset, we split the clients into $M$ groups. A client $c$ in group $m$ is provided with data where data $m$ accounts for over $q$ percent. Within the same group, data are uniformly distributed among all the clients. The parameter $q$ controls the distribution inference of clients' local training data. If $q=\frac{1}{M}$, the clients' local training data are independent and identically distributed. We evaluate our FLPhish(weight) on three different $q$: 0.1 (IID), 0.2, 0.5, 0.6, 0.7, and 0.8.
  \subsubsection{{\textit{The number of clients}}} The number of clients is set to be 50 in our experiment.
  \subsubsection{{\textit{The local CNN model used by clients}}} ResNet is employed to perform deep learning tasks in our local client.
  \subsubsection{{\textit{The datasets {$d$}}}} We take three different datasets as our experiment datasets: \begin{itemize}
      \item MNIST: MNIST is a 10-class digit image classification dataset consisting of 60,000 training examples and 10,000 testing examples.
      \item Fashion-MNIST: Fashion-MNIST is a 10-class fashion image classification dataset. It has a predefined training set of 60,000 fashion images and a testing set of 10,000 fashion images.
      \item CIFAR-10: CIFAR-10 is a color image classification dataset. It has predefined 50,000 training examples and 10,000 testing examples. Each example belongs to one of the 10 classes.
  \end{itemize}

@@

  \par Each client has 1,000 samples taken from the training dataset. Among the samples, 800 of them are used as training datasets, while another 200 are taken as test datasets. And the server has 10000 testing examples from the testing dataset. 
  \subsubsection{\textit{Evaluated Byzantine Attacks}} We evaluate our FLPhish(weight) against two Byzantine attacks:
  \begin{itemize}
    \item Untargeted Byzantine Attacks: For each Byzantine client, it mislabels the data $l$ to $(l-1)\ mod\ M$ to launch the attacks against FLPhish(weight). The attack is known as the Label-flipping attack. 
    \item Random Byzantine Attacks: For each Byzantine client, it mislabels the labels by returning a randomly chosen result.
    \end{itemize}

@@

  \subsection{Performance Comparison under Random Attacks}
  From Fig. \ref{fig_exp_extreme}-\ref{fig_table_byzantines_random}, we can see that random Byzantine attacks have poor performance against FLPhish(weight) and FLPhish($\tau$=0.1, 0.2). We refer from the result that a random Byzantine attack has a drawback that it can not gather its influence at one data point as untargeted Byzantine attackers do. Meanwhile, we can see that it has good results in attacking FLPhish($\tau$=0.5) in the CIFAR-10 dataset. From Fig. \ref{fig_exp_reputation}, we can see that the reputation of benign clients in CIFAR-10 experiments rapidly falls under the threshold of 0.5 due to the complexity of the tasks. With the increase of imbalance degree value $q$, the reputation of the benign clients falls more rapidly in the experiments of the CIFAR-10 dataset than in the experiments of the MNIST and the Fashion-MNIST dataset. As benign clients' reputations in the experiments of the CIFAR-10 dataset become under the threshold $\tau$ of 0.5, they are identified as malicious Byzantine clients as well. As many benign clients are falsely identified as Byzantine attackers, the FL server lacks enough trusted FL clients to assist the aggregation, therefore causing a bad performance of FLPhish($\tau$=0.5). Meanwhile, we can see that FLPhish($\tau$=0.1), FLPhish($\tau$=0.2), and FLPhish(weight) stood still against the random Byzantine attacks. The results indicate that the value of the threshold $\tau$ should be considered carefully in the application in some complex tasks.

  \subsection{{Performance Comparison under Untargeted Attacks}} We further evaluate FLPhish(weight) towards untargeted Byzantine attacks in Ensemble FL.

    \subsubsection{\ul{Performance Comparison with Different Distributions}} We evaluate our FLPhish(weight) under the experiment setting where the Byzantine client portion is a fixed value of 0.5 and distribution imbalance value $q$ is different across the experiments. The experiment results are shown in Fig. \ref{fig_table_imbalances_untargeted}. We can observe that both the FLPhish($\tau$=0.1,0.2,0.5) and FLPhish(weight) outperform baseline until the imbalance degree $q$ reaches 0.8. The imbalance degree $q$ of 0.8 means that the distribution of data becomes extremely non-IID. The performance of the FLPhish($\tau$=0.5) rapidly falls in this case. When facing the distribution of imbalance degree $q=0.8$, each client performs badly, bringing a decline to its reputation. The rise of imbalance degree brings an explosive decline in the global model's accuracy. The accuracy of the global model under the FLPhish($\tau$=0.5) stays to be 0.1 in the whole learning process. It means that the FLPhish($\tau$=0.5) identifies all the clients as Byzantine clients, making the aggregation process invalid. We can see that the FLPhish($\tau$=0.2) outperforms others. When the distribution becomes non-IID, the threshold of FLPhish($\tau$) should be set to a lower value to avoid a high false-negative rate. In the experiment of MNIST, it should be set to 0.2. Meanwhile, the performance of FLPhish(weight) remains stable under different imbalance degrees.

    \subsubsection{\ul{Performance Comparison with Different Fractions of Byzantine Clients}} Different fractions of Byzantine clients are taken into account as well. Figure. \ref{fig_table_byzantines_untargeted} shows that the accuracy for FedAvg, Median and Trimmed Mean begins to fall rapidly when the Byzantine portion reaches nearly 50\%. Furthermore, FedAvg, Median, and Trimmed Mean perform extremely invalidly (the accuracy falls below 1\%) when encountered with high fractions of Byzantine attackers. In comparison, FLPhish($\tau$) and FLPhish(weight)'s performance under various thresholds maintain a high level of performance as the portion grows. Both FLPhish($\tau$) and FLPhish(weight) effectively detect Byzantine clients and accurately discard them from the aggregation process. The global model can be successfully trained without the involvement of Byzantine clients during the aggregation procedures. Furthermore, the data show that FLPhish($\tau$=0.1) performs worse than the other two. This is since the threshold=0.1 is far too low to adequately detect Byzantine clients. Though the Byzantine attackers try to make the right predictions of the public dataset and then send the opposite wrong predictions to the FL server. But they also make wrong predictions first and coincidentally transfer the opposite right predictions to the FL server. Thus the reputation values of some Byzantine clients, in particular, can exceed 0.1. It indicates that if the threshold is not well set, Byzantine clients can avoid being detected by FLPhish($\tau$=0.5). As the fractions of Byzantine clients go over the threshold of 50\%, the harm brought by untargeted Byzantine attacks increase rapidly for they outnumber the fractions of the benign clients. In the meantime, FLPhish(weight) shows stable performance whenever the fractions of Byzantine clients are.

    \subsection{{Experiment Result Analysis}} Our experiment results demonstrate that both FLPhish($\tau$) and FLPhish(weight) outperform FedAvg, Median \cite{ref_13_defense} and Trimmed Mean \cite{ref_13_defense} on defending against Byzantine attacks in FL. The results also show that the threshold setup has a significant impact on the performance of the FLPhish($\tau$). Only when the managers of FL servers have complete knowledge of FL clients (the imbalance degree of each client), can they accurately set the value of the threshold suitably. However, it is not feasible due to the privacy concern of FL. FLPhish(weight), on the other hand, remains constant regardless of the circumstances. FLPhish(weight) can let clients with higher performance have a stronger influence on the aggregation process by using the reputation value as the weight. To summarize, FLPhish(weight) is a better and more stable aggregation technique than FLPhish(weight) and demonstrates to be a more practical Byzantine defense framework.

@@

In this paper, we have designed an FL architecture, Ensemble Federated Learning in this study, which allows knowledge transferring between the FL server and FL clients via the unlabeled dataset and FL clients' predictions of it. We have crafted the FLPhish technique to make Ensemble FL resistant to Byzantine attacks by using a labeled dataset as `bait' to detect malicious Byzantine clients. Furthermore, we have proposed a reputation technique based on Bayesian inference to determine a client's level of trust. We have also presented an aggregation techniques, FLPhish-weight, to improve FLPhish's performance. At last, we have tested our suggested FLPhish in a variety of scenarios. The results of the experiment demonstrates the comparable performance of FLPhish in terms of accuracy and robustness under Byzantine attacks in FL. 
\par Our future work will focus on evaluating FLPhish against more advanced Byzantine attacks and improving FLPhish scheme's efficiency.
